---
title: "HelloGIS"
author: "jbjares"
date: "Tuesday, May 26, 2015"
output: ioslides_presentation
---

## Summary
This is a reproducible paper, that tries to introduce the reader on friendly "hello world Gis", using some R packages, who I'd like to highlight is from Robinlovelace's studies who could be found at https://github.com/Robinlovelace?tab=repositories.
Thanks Robin.


## Preparing Environment - Install Packages - 1/2
```{r, installPackages_first, cache=TRUE, echo=TRUE, eval=FALSE}

# The order is important here, take care.

#1) Creating a vector with the name of the basic packages to install
pkgs <- c("devtools", "shiny", "rgdal",
          "rgeos", "ggmap", "raster")


#2) Install these packages over the vector
install.packages(pkgs, repos = "http://cran.us.r-project.org")
```


## Preparing Environment - Install Packages - 2/2
```{r, installPackages_second, cache=TRUE, echo=TRUE, eval=FALSE}

#3) Import devtools library
library(devtools)

#4) Creating a second vector with the name of robinlovelace's packages. 
#Thanks Robin :)
gh_pkgs <- c("rstudio/leaflet", 
             "robinlovelace/stplanr") 


#5) Install them
install_github(gh_pkgs)


#6) Attach them to library
lapply(c(pkgs, "leaflet", "stplanr"), 
       library, character.only = T)

```


## A global var (named: downloadLink), as an example
```{r, defineDowloadingLink, cache.vars='downloadLink',cache=TRUE, echo=TRUE, eval=FALSE }
downloadLink <- paste0("http://www.eurogeographics.org",
                       "/sites/default/files/",
                       "EBM_v91_sample_shape.zip")
```
- See the correlation between cache.vars='downloadLink' and the variable name on the snippet Above.


## Downloading data

```{r,dowloadingLink, cache=TRUE, echo=TRUE, eval=FALSE}
download.file(downloadLink, paste0(getwd(),"/data.zip"))

```


## Unziping data
```{r,unzipData, cache=TRUE, echo=TRUE, eval=FALSE}
unzip("data.zip")
```


## Reading The shape file
```{r,readShape, cache=TRUE, echo=TRUE, eval=FALSE}

lnd <- shapefile("./EBM_v91_sample/StatisticalUnits/NUTS_3.shp")

```


## Showing The data content
```{r,showClassDataContent, cache=TRUE, echo=TRUE, eval=TRUE}
print(class(lnd)) 
```


## Using google geocode to access NUIG location
```{r,getNuigLocation, cache=TRUE, echo=TRUE, eval=TRUE, cache.vars='locationNUIG'}
locationNUIG <- geocode("NUIG",sensor = TRUE)
```

## Using Robinlovelace API to do the great magic :)
```{r,theMagic, cache=FALSE, echo=TRUE, eval=TRUE}
library(leaflet)
mp <- leaflet(data=locationNUIG)
mp <- addTiles(map = mp)
mp <- addCircles(mp, radius = 40)
mp <- addPopups(mp,popup = "That's NUIG :)")
mp
```

## References
- http://ec.europa.eu/eurostat/data/database
- http://census.cso.ie/censusasp/saps/boundaries/ED_SA%20Disclaimer1.htm
- http://census.cso.ie/censusasp/saps/boundaries/Census2011_NUTS3_generalised20m.zip
- http://www.eurogeographics.org/products-and-services/euroboundarymap
- http://www.r-bloggers.com/the-leaflet-package-for-online-mapping-in-r/
- https://rstudio.github.io/leaflet/
- https://github.com/Robinlovelace?tab=repositories


## Conclusion
That's can be basic, rudimentary but need to be shared, because is very fun!
Thank you :)

